Report on Certificate Tools

### 2016-08-30 TEX/draft.tex
Started on Keytool Chapter

>>>>

  \subsection{Type}
  Keytool has native support for both PKCS\#12 and Java KeyStore type files 
  \subsection{View and information}
  To view information about PEM or DER encoded certificate use:
  \begin{verbatim}
  keytool -printcert -file certificate.extention
  \end{verbatim}

  To view information about Jave KeyStore or PKCS\#12 encoded file use:
  \begin{verbatim}
  keytool -list -v -keystore store_file.[pfx|p12|jks]
  \end{verbatim}

  Viewing Public key part of certificate is not availiable in keytool.
  \subsection{License}
